Maintenance planning on French military aircraft operations

### 2018-06-26 R/presentations/MOSIM_presentation/presentation.Rmd
ppt MOSIM

* The present model deals with an heterogeneus fleet, with different standards and capacities.
* Multiple objectives have been incorporated in order to satisfy the French Air Force's specific needs.
* This model also features several improvements in the MIP modelling that permit greater instance sizes.

@@

* Analysis for all instances: not many pareto optimal points available (between two and four).
* The objectives are quite aligned one with the other.

# Next steps
## Next steps

* **Try different objective formulations**: availability - maintenability - future state.
* **Try more linent objectives**: relax the `max` in the objective.
* **Break symmetries**: clustering candidates, fixing end availabilities.
* **Add more constraints**: minimal duration of assignments, storage of aircraft.

>>>>

* The present model deals with an heterogeneous fleet, with different standards and capacities.
* Multiple objectives have been incorporated in order to satisfy the French Air Force's specific needs.
* This model also features several improvements in the MIP modelling that permit greater instance sizes.

@@

* Analysis for all instances: not many Pareto optimal points available (between two and four).
* The objectives are quite aligned one with the other.

# Current and next steps

## Current steps

* **Linent objectives**: minimized total number of maintenances with a hard maximum on total maintenances per month.
* **Multiple solvers**: GUROBI, CPLEX, CBC, CPO, CHOCO.

## Next steps

* **Try different objective formulations**: availability - maintenability - future state.
* **Break symmetries**: clustering candidates, fixing end availabilities.
* **Add more constraints**: minimal duration of assignments, storage of aircraft.
* **Compare solvers exhaustively**: to determine when each one can be advantageous.
